Euler's polyhedron formula

### 2016-02-25 mandatory_assignment/main.tex
assignment done

\usepackage[]{enumerate} 
\usepackage[]{pst-platon} 
\usepackage[]{graphicx}

@@

Eminent mathematician Leonhard Euler proved that the problem stated above has
no solution. In working with the solution to this problem however, he dabbled
in a type of mathematics later to be known as \emph{graph theory}. One of the
more remarkable results (in my humble opinion) to arise from this new field of
mathematics is the discovery of a relationship between the number of vertices,
edges and faces in a polyhedron. It is exactly this relationship that Euler's
polyhedron formula captures.

\begin{theorem}[Euler's polyhedron formula]
    Any convex polyhedron's surface satisfies the equation
    \begin{equation}
        \notag
        V - E + F = 2
    \end{equation}
    where $V$, $E$ and $F$ denote the number of vertices, edges and faces,
    respectively.
\end{theorem}
\section{Preliminaries}
\label{sec:preliminaries}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{drawing.pdf}
    \caption{First iterations of proof; using a cube.}
    \label{fig:proof}
\end{figure}

@@

\begin{thebibliography}{9}
    \bibitem{proofs}
        http://www.ics.uci.edu/~eppstein/junkyard/euler/all.html
\end{thebibliography}
\end{document}

>>>>

\usepackage[]{enumerate} 
\usepackage[]{pst-platon} 
\usepackage[]{graphicx} 
\usepackage[]{url} 
\urlstyle{sf}

@@

Eminent mathematician Leonhard Euler proved that the problem stated above has
no solution. In working with the solution to this problem however, he dabbled
in a type of mathematics later to be known as \emph{graph theory}. One of the
more remarkable results (in my opinion) to arise from this new field of
mathematics is the discovery of a relationship between the number of vertices,
edges and faces in a polyhedron. It is exactly this relationship that Euler's
polyhedron formula captures.

\begin{theorem}[Euler's polyhedron formula]
    Any convex polyhedron's surface satisfies the equation
    \begin{equation}
        \notag
        V - E + F = 2
    \end{equation}
    where $V$, $E$ and $F$ denote the number of vertices, edges and faces,
    respectively.
\end{theorem}

The reason I chose this specific theorem is because it was one of my first
encounters with something resembling pure mathematics than the kind of
mathematics I had been exposed to during elementary school. Having always been
a fan of puzzles, I especially liked this result since it sprung from a
seemingly ''innocent'' looking question that everyday people would walk around
pondering.

\section{Preliminaries}
\label{sec:preliminaries}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{drawing.pdf}
    \caption{First iterations of proof; using a cube. Image retrieved from \cite{image}.}
    \label{fig:proof}
\end{figure}

@@

\section{Applications}
\label{sec:applications}

Direct applications of the polyhedron formula can be hard to find. However, its
generalizations to other mathematical fields as topology gives us an indication
as to what kind of topological object we are working with. The \emph{euler
characteristic}, denoted $\chi$, is a topological invariant. In this more
general sense, our polyhedron formula reads $\chi = V - E + F$, where $\chi =
2$. This characteristic can for instance be used to classifly the platonic
solids. \cite{chi} presents a lot of mathematical results using the euler
characteristic.

\begin{thebibliography}{2}
    \bibitem{proofs}
        \url{http://www.ics.uci.edu/~eppstein/junkyard/euler/all.html}
    \bibitem{image}
        \url{https://en.wikipedia.org/wiki/Euler_characteristic#/media/File:V-E%2BF%3D2_Proof_Illustration.svg}
    \bibitem{chi}
        \url{https://en.wikipedia.org/wiki/Euler_characteristic}
\end{thebibliography}
\end{document}
